Implementing Real-Time Transport Services over an Ossified Network

### 2016-05-23 paper.tex
Expands discussion of TCP Hollywood

\documentclass{sig-alternate-05-2015}
\usepackage[l2tabu,orthodox]{nag}
\usepackage[utf8x]{inputenc}
\usepackage[british]{babel}
\usepackage[babel=true]{microtype}
\usepackage{amsmath}
\usepackage[all]{onlyamsmath}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{upquote}
\usepackage{graphicx}
\usepackage{url}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{bytefield}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\usepackage{balance}
\usepackage{tabularx}
\usepackage{xspace}

\newcommand{\ie}{{i.e.}\xspace}
\newcommand*\rot{\rotatebox{90}}

@@

The work in TAPS provides a vocabulary for discussing the components of
transport protocols.  The vocabulary is useful when discussing the needs of
real-time applications, and the protocols to support them.

Timing is the most salient feature of real-time applications. Since their data
must be conveyed with real-time demands, they all have some concept of a
\emph{deadline}. Data that fails to present within the deadline is otherwise
useless.
% Deadlines may be short or long.
The `slack' in a deadline depends on the application. Interactive applications,
such as telephony, video conferencing, or telepresence, require low end-to-end
latency. Their deadlines for presenting the media, \ie playing the audio and
displaying the video frame, range from tens to a few hundred milliseconds.
Non-interactive application deadlines associated with broadcast and on-demand
programming are on the order of seconds.
% , such as broadcast TV, may have deadlines on the order of seconds,
% or even tens of seconds for on-demand programming.

Networked multimedia deadlines are unusual when compared to other real-time
systems. They are simultaneously flexible and strict: flexible in that the exact
value of the deadline is typically not important, provided it is of the right
order-of-magnitude for the application, but strict in that any particular
deadline provides a hard cut-off, after which the data is useless. \todo{this
para is largely unconvincing -- flexible is fine; strict is less believable, \ie
how are RT systems any different when the deadline expires? (Many RTSs will
discard, too.)}

>>>>

\documentclass{sig-alternate-05-2015}
\usepackage[l2tabu,orthodox]{nag}
\usepackage[utf8x]{inputenc}
\usepackage[british]{babel}
\usepackage[babel=true]{microtype}
\usepackage{amsmath}
\usepackage[all]{onlyamsmath}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{upquote}
\usepackage{graphicx}
\usepackage{url}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{bytefield}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{color}
\usepackage{balance}
\usepackage{tabularx}

\newcommand*\rot{\rotatebox{90}}

@@

The work in TAPS is valuable, because it gives us a vocabulary for
discussing the components of transport protocols.  We can then use that
vocabulary when discussing the needs of real-time applications, and the
protocols needed to support those needs.

The essential feature of real-time applications is clearly timing. That is,
since these applications convey real-time data, they all have some concept
of a \emph{deadline} by which that data must be presented, after which it
becomes useless.
The deadline might be short or long. Interactive applications, such as
telephony, video conferencing, or telepresence, require low end-to-end
latency, with the deadline for presenting the media (playing the audio,
displaying the video frame) being tens, or perhaps low hundreds, of
milliseconds after it was captured. Non-interactive applications, such as
broadcast TV, may have deadlines in the order of seconds, or even tens of
seconds for on-demand programming.
The deadlines in many networked multimedia applications are unusual when
compared to other real-time systems. They are simultaneously flexible and
strict: flexible in that the exact value of the deadline is typically not
important, provided it is of the right order-of-magnitude for the
application, but strict in that any particular deadline provides a hard
cut-off, after which the data is useless.
